An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/main.tex
Unrolling lamport's 1-bit algorithm.
Included experiments by Filip.
Drew Petri net for Lamport's algorithm in tikz

\begin{center}
  \includegraphics[width=10cm]{lamport}
\end{center}

@@

\begin{center}
\begin{tikzpicture}[node distance=1cm]
  \node[transition, label=left:t1] (t1) {};
  \node[place, tokens=1, label=left:a, below of=t1] (a) {};
  \node[transition, label=left:t2, below of=a] (t2) {};
  \node[place, tokens=0, label=left:b, below of=t2] (b) {};
  \node[place, tokens=0, label=right:$\neg bit2$, right of=t2] (nbit2) {};
  \draw (t1) edge[pre, bend left, min distance=2cm, out=225, in=-45] (b);
  \draw (t1) edge[post] (a);
  \draw (t2) edge[pre] (nbit2);
  \draw (t2) edge[post] (nbit2);
  \draw (t2) edge[pre] (a);
  \draw (t2) edge[post] (b);
\end{tikzpicture}
\end{center}

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
    \node[print, right=of satc] (yes) {N satisfies P};
    \node[print, below=of satc] (dontknow) {Don't know};
    \node[state, right=of yes] (end1) {END};
    \node[state, below=of dontknow] (end2) {END};

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                               	$C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                    	$\delta:=\Delta(A_\theta)$\\
                                    	$C:=C \cup \{\delta\}$};
  \node[print, right=of satc] (yes) {N satisfies P};
  \node[print, right=of satctheta] (dontknow) {Don't know};
  \node[state, right=of yes] (end1) {END};
  \node[state, right=of dontknow] (end2) {END};

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C':=\mathcal C'(N, \neg P)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C')$};
    \node[print, right=of satc] (noinv) {No Invariant};
    \node[action, below=of satc] (inv) {$A':=\text{Model}(C')$\\
      $I := \text{Inv}(N, A')$};
    \node[print, below=of inv] (printinv) {Invariant: $I$};
    \node[state, right=of noinv] (end1) {END};
    \node[state, below=of printinv] (end2) {END};

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C':=\mathcal C'(N, \neg P)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C')$};
    \node[print, right=of satc] (noinv) {No Invariant};
    \node[action, below=of satc] (model1) {$A':=\text{Model}(C')$};
    \node[action, below=of model1] (cm) {$C_M:=\text{MinConstraints}(N, A')$};
    \node[decision, below=of cm] (satcm) {$\text{SAT}(C' \cup C_M)$};
    \node[action, right=of satcm] (model2) {$A':=\text{Model}(C' \cup C_M)$};
    \node[action, below=of satcm] (inv) {$I := \text{Inv}(N, A')$};
    \node[print, below=of inv] (printinv) {Invariant: $I$};
    \node[state, right=of noinv] (end1) {END};
    \node[state, below=of printinv] (end2) {END};

@@

\begin{figure}
\begin{tikzpicture}
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$\\
                                        $D:=\{\}$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                                        $C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                                $\delta:=\Delta(A_\theta)$\\
                                                $C:=C \cup \{\delta\}$\\
                                                $D:=D \cup \{\delta\}$};
  \node[print, right=of satctheta] (noinv2) {No Invariant};
  \node[state, below=of noinv2] (end3) {END};

>>>>

\begin{figure}
\begin{center}
  \begin{tikzpicture}
  \draw[box] (-2,8.5) rectangle (1,0);
  \draw[box] (3,8.5) rectangle (7.5,0);

  \node at (-0.5, 0.5) {First Process};
  \node at (5, 0.5) {Second Process};

  \node[place, label=left:p3] (p3) at (0,7) {};
  \node[transition, label=left:u1] (u1) at (0,6) {};
  \node[place, tokens=1, label=left:p1] (p1) at (0,5) {};
  \node[transition, label=left:u2] (u2) at (0,4) {};
  \node[place, label=left:p2] (p2) at (0,3) {};
  \node[transition, label=left:u3] (u3) at (0,2) {};

  \draw (p3) edge[flow] (u1);
  \draw (u1) edge[flow] (p1);
  \draw (p1) edge[flow] (u2);
  \draw (u2) edge[flow] (p2);
  \draw (p2) edge[flow] (u3);
  \draw[rounded corners=4mm] (u3) |- (-1.5,1) -- (-1.5,8) [flow] -| (p3);

  \node[transition, label=above:v1] (v1) at (4,7) {};
  \node[place, label=right:q3] (q3) at (4,6) {};
  \node[transition, label=right:v2] (v2) at (4,5) {};
  \node[place, label=right:q4] (q4) at (4,4) {};
  \node[transition, label=left:v3] (v3) at (4,3) {};

  \node[place, label=right:q2] (q2) at (5.5,7) {};
  \node[transition, label=right:v4] (v4) at (5.5,6) {};
  \node[place, label=right:q5] (q5) at (5.5,5) {};
  \node[transition, label=right:v5] (v5) at (5.5,4) {};
  \node[place, tokens=1, label=right:q1] (q1) at (5.5,3) {};
  \node[transition, label=right:v6] (v6) at (5.5,2) {};

  \draw (q2) edge[flow] (v4);
  \draw (v4) edge[flow] (q5);
  \draw (q5) edge[flow] (v5);
  \draw (v5) edge[flow] (q1);
  \draw (q1) edge[flow] (v6);
  \draw[rounded corners=4mm] (v6) |- (7,1) -- (7,8) [flow] -| (q2);

  \draw (q2) edge[flow] (v1);
  \draw (v1) edge[flow] (q3);
  \draw (q3) edge[flow] (v2);
  \draw (v2) edge[flow] (q4);
  \draw (q4) edge[flow] (v3);
  \draw (v3) edge[flow] (q1);

  \node[place, label=above:bit1] (bit1) at (2,6) {};
  \node[place, label=below:$\neg$bit1] (nbit1) at (2,4) {};
  \node[place, label=below:$\neg$bit2] (nbit2) at (2,2) {};

  \draw (bit1) edge[flow] (u1);
  \draw (u1) edge[flow] (nbit1);
  \draw (nbit1) edge[flow] (u2);
  \draw (u2) edge[flow] (bit1);
  \draw (v1) edge[flow, <->] (bit1);
  \draw (nbit1) edge[flow, <->, bend left=18] (v4);
  \draw (nbit1) edge[flow, <->] (v3);
  \draw (nbit2) edge[flow, <->] (u3);
  \draw (v2) edge[flow] (nbit2);
  \draw (v5) edge[flow, bend left=30] ([xshift=-0.2mm, yshift=1mm] nbit2.east);
  \draw (nbit2) edge[flow] (v6.west);
\end{tikzpicture}
\end{center}
\caption{Petri net for Lamport's 1-bit algorithm}
\label{fig:lamport-petri-net}
\end{figure}

@@

\begin{figure}
\begin{center}
\begin{tikzpicture}
  \node[transition, label=left:t1] (t1) at (0,5) {};
  \node[place, tokens=1, label=left:a] (a) at (0,4)  {};
  \node[transition, label=left:t2] (t2) at (0,3)  {};
  \node[place, tokens=0, label=left:b] (b) at (0,2)  {};
  \node[place, tokens=0, label=below:$\neg$bit2] (nbit2) at (2,3) {};
  \draw (t1) edge[flow] (a);
  \draw (a) edge[flow] (t2);
  \draw (t2) edge[flow] (b);
  \draw (nbit2) edge[flow, <->] (t2);
  \draw[rounded corners=4mm] (b) |- (-1.5,1) -- (-1.5,6) [flow] -| (t1);
\end{tikzpicture}
\end{center}
\caption{Subnet of Petri net for Lamport's 1-bit algorithm}
\label{fig:lamport-petri-net-subnet}
\end{figure}

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
    \node[print, right=of satc] (yes) {N satisfies P};
    \node[print, below=of satc] (dontknow) {Don't know};
    \node[state, right=of yes] (end1) {END};
    \node[state, below=of dontknow] (end2) {END};

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                               	$C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                    	$\delta:=\Delta(A_\theta)$\\
                                    	$C:=C \cup \{\delta\}$};
  \node[print, right=of satc] (yes) {N satisfies P};
  \node[print, right=of satctheta] (dontknow) {Don't know};
  \node[state, right=of yes] (end1) {END};
  \node[state, right=of dontknow] (end2) {END};

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C':=\mathcal C'(N, \neg P)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C')$};
    \node[print, right=of satc] (noinv) {No Invariant};
    \node[action, below=of satc] (inv) {$A':=\text{Model}(C')$\\
      $I := \text{Inv}(N, A')$};
    \node[print, below=of inv] (printinv) {Invariant: $I$};
    \node[state, right=of noinv] (end1) {END};
    \node[state, below=of printinv] (end2) {END};

@@

\begin{figure}
\begin{center}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
    \node[state] (begin) {BEGIN};
    \node[action, below=of begin] (c) {$C':=\mathcal C'(N, \neg P)$};
    \node[decision, below=of c] (satc) {$\text{SAT}(C')$};
    \node[print, right=of satc] (noinv) {No Invariant};
    \node[action, below=of satc] (model1) {$A':=\text{Model}(C')$};
    \node[action, below=of model1] (cm) {$C_M:=\text{MinConstraints}(N, A')$};
    \node[decision, below=of cm] (satcm) {$\text{SAT}(C' \cup C_M)$};
    \node[action, right=of satcm] (model2) {$A':=\text{Model}(C' \cup C_M)$};
    \node[action, below=of satcm] (inv) {$I := \text{Inv}(N, A')$};
    \node[print, below=of inv] (printinv) {Invariant: $I$};
    \node[state, right=of noinv] (end1) {END};
    \node[state, below=of printinv] (end2) {END};

@@

\begin{figure}
  \begin{tikzpicture}[
      every path/.style={draw, ->, >=stealth, shorten >=2pt, shorten <=2pt}
    ]
  \node[state] (begin) {BEGIN};
  \node[action, below=of begin] (c) {$C:=\mathcal C(N)$\\
                                        $D:=\{\}$};
  \node[decision, below=of c] (satc) {$\text{SAT}(C \cup \{\neg P\})$};
  \node[action, below=of satc] (modelc) {$A:=\text{Model}(C \cup \{\neg P\})$\\
                                        $C_{\theta}:=\text{TrapConditions}(N, A)$};
  \node[decision, below=of modelc] (satctheta) {$\text{SAT}(C_\theta)$};
  \node[action, below=of satctheta] (modelctheta) {$A_\theta:=\text{Model}(C_\theta)$\\
                                                $\delta:=\Delta(A_\theta)$\\
                                                $C:=C \cup \{\delta\}$\\
                                                $D:=D \cup \{\delta\}$};
  \node[print, right=of satctheta] (noinv2) {No Invariant};
  \node[state, below=of noinv2] (end3) {END};
